A Rough Guide to Pre-processing High-Frequency Animal Tracking Data

### 2020-10-16 02_filtering_data.Rmd
clean up figures

@@

```{r}
# define a four colour palette
pal <- RColorBrewer::brewer.pal(3, "PRGn")
```

@@

```{r}
# make figure of canonical data with added errors
figure_raw <-
  ggplot()+
  geom_point(data = data_copy,
            aes(x, y),
            col = "grey",
            alpha = 1,
            size = 0.2)+
  geom_path(data = data,
            aes(x, y),
            col = "grey20",
            alpha = 1)+
  ggthemes::theme_few()+
  theme(axis.text = element_blank(),
        axis.title = element_blank(),
        panel.background = element_rect(fill = "white"))+
  coord_equal()+
  labs(colour = NULL)
```

@@

```{r}
# plot data inside and outside bbox
fig_filter_bounds <-
  ggplot()+
  geom_point(data = data_inside_bbox,
             aes(x, y),
             col = pal[3],
             alpha = 1, size = 0.2)+
  geom_point(data = data_copy[!data_inside_bbox,
                              on = c("x", "y")],
             aes(x, y),
             col = "grey",
             alpha = 0.5, size = 0.2)+
  geom_path(data = data,
            aes(x, y),
            col = "grey20",
            alpha = 1)+
  geom_hline(yintercept = c(0.5, 1),
             col = "grey",
             lty = 2)+
  ggthemes::theme_few()+
  theme(axis.text = element_blank(),
        axis.title = element_blank(),
        panel.background = element_rect(fill = "white"))+
  theme(plot.background = element_rect(fill = NA))+
  coord_equal(expand = T)

@@

```{r}
# data plot
fig_outlier_remove <-
  ggplot()+
  geom_path(data = data_copy,
            aes(x, y),
            col = "grey",
            lwd = 0.2)+
  geom_point(data = data_copy[500:800, ],
             aes(x, y),
             shape = 2, col = pal[1])+
  geom_point(data = data_copy[!data_copy[500:800, ],
                              on = c("x", "y")],
             aes(x, y, 
                 col = (in_speed >= 0.03 & out_speed >= 0.03),
                 shape = (in_speed >= 0.03 & out_speed >= 0.03)),
             show.legend = F,
             alpha = 0.5)+
  geom_path(data = data,
            aes(x, y),
            col = "grey20",
            alpha = 1)+
  ggthemes::theme_few()+
  theme(axis.text = element_blank(),
        axis.title = element_blank(),
        panel.background = element_rect(fill = "white"))+
  scale_color_manual(values = c(pal[3], "black"))+
  scale_shape_manual(values = c(16, 21))+
  coord_equal()+
  theme(plot.background = element_rect(fill = NA))
```

@@

```{r}
# get plots
fig_reflection <-
  ggplot()+
    geom_path(data = reflection,
             aes(x, y),
             alpha = 1,
             col = "grey",
             lwd = 0.2)+
  geom_point(data = reflection,
             aes(x, y),
             alpha = 0.5,
             col = "grey",
             fill = pal[2],
             shape = 21)+
  geom_point(data = data_no_reflection,
             aes(x, y),
             alpha = 0.5,
             colour = pal[3],
             shape = 16,
             show.legend = F)+
  geom_path(data = data,
            aes(x, y),
            col = "grey20",
            alpha = 1)+
  ggthemes::theme_few()+
  theme(axis.text = element_blank(),
        axis.title = element_blank(),
        panel.background = element_rect(fill = "white"))+
  coord_equal()+
  theme(plot.background = element_rect(fill = NA))

>>>>

```{r}
data_copy <- fread("data/data_errors.csv")
```

@@

```{r}
# define a four colour palette
pal <- RColorBrewer::brewer.pal(4, "Set1")
```

@@

```{r}
# make figure of canonical data with added errors
figure_raw <-
  ggplot()+
  geom_point(data = data_copy,
            aes(x, y),
            col = "grey",
            alpha = 1,
            size = 0.2)+
  geom_path(data = data,
            aes(x, y),
            col = "grey20",
            alpha = 1)+
  ggthemes::theme_few()+
  theme(axis.text = element_blank(),
        axis.title = element_blank())+
  coord_equal()+
  labs(colour = NULL)
```

@@

```{r}
# plot data inside and outside bbox
fig_filter_bounds <-
  ggplot()+
  geom_point(data = data_inside_bbox,
             aes(x, y),
             col = pal[3],
             alpha = 1, size = 0.2)+
  geom_point(data = data_copy[!data_inside_bbox,
                              on = c("x", "y")],
             aes(x, y),
             col = "grey",
             alpha = 0.5, size = 0.2)+
  geom_path(data = data,
            aes(x, y),
            col = "grey20",
            alpha = 1)+
  geom_hline(yintercept = c(0.5, 1),
             col = "grey",
             lty = 2)+
  ggthemes::theme_few()+
  theme(axis.text = element_blank(),
        axis.title = element_blank())+
  theme(plot.background = element_rect(fill = NA))+
  coord_equal(expand = T)

@@

```{r}
# data plot
fig_outlier_remove <-
  ggplot()+
  geom_path(data = data_copy,
            aes(x, y),
            col = "grey",
            lwd = 0.2)+
  geom_point(data = data_copy[500:800, ],
             aes(x, y),
             size = 0.2,
             shape = 2, col = pal[4])+
  geom_point(data = data_copy[!data_copy[500:800, ],
                              on = c("x", "y")],
             aes(x, y, 
                 col = (in_speed >= 0.03 & out_speed >= 0.03),
                 shape = (in_speed >= 0.03 & out_speed >= 0.03)),
             show.legend = F,
             alpha = 0.5)+
  geom_path(data = data,
            aes(x, y),
            col = "grey20",
            alpha = 1)+
  ggthemes::theme_few()+
  theme(axis.text = element_blank(),
        axis.title = element_blank())+
  scale_color_manual(values = c(pal[3], "black"))+
  scale_shape_manual(values = c(16, 21))+
  coord_equal()+
  theme(plot.background = element_rect(fill = NA))
```

@@

```{r}
# get plots
fig_reflection <-
  ggplot()+
    geom_path(data = reflection,
             aes(x, y),
             alpha = 1,
             col = "grey",
             lwd = 0.2)+
  geom_point(data = reflection,
             aes(x, y),
             alpha = 0.5,
             col = "grey40",
             fill = "grey",
             shape = 21)+
  geom_point(data = data_no_reflection,
             aes(x, y),
             alpha = 0.5,
             colour = pal[3],
             shape = 16,
             show.legend = F)+
  geom_path(data = data,
            aes(x, y),
            col = "grey20",
            alpha = 1)+
  ggthemes::theme_few()+
  theme(axis.text = element_blank(),
        axis.title = element_blank())+
  coord_equal()+
  theme(plot.background = element_rect(fill = NA))

### 2020-10-16 05_calibration_data.Rmd
clean up figures

```{r}
# plot data
fig_data_bbox <-
  ggplot()+
  geom_path(data = data_raw,
            aes(x, y),
             col = "grey", alpha = 0.5, size = 0.3)+
  geom_point(data = data_raw,
             aes(x, y,
                 col = x > 645000),
             alpha = ifelse(data_raw$x > 645000, 0.5, 1),
             size = ifelse(data_raw$x > 645000, 0.3, 2),
             show.legend = F)+
  scale_colour_manual(values = c("grey", pal[3]))+
  geom_vline(xintercept = 645000,
             col = "grey", lty = 2)+
  ggspatial::annotation_scale(location = "br")+
  ggthemes::theme_few()+
  theme(axis.text = element_blank(),
        axis.title = element_blank(),
        panel.background = element_rect(fill = "white"))+
  coord_sf(crs = 32631)

@@

```{r}
# plot filtered data
fig_speed_outliers <-
  ggplot()+
  geom_point(data = data,
             aes(x, y, 
                 col = speed_in < 25.6),
             size = 0.3, alpha = 0.5,
             show.legend = F)+
  scale_color_manual(values = c("grey", pal[3]))+
  ggthemes::theme_few()+
  theme(axis.text = element_blank(),
        axis.title = element_blank(),
        panel.background = element_rect(fill = "white"))+
  ggspatial::annotation_scale(location = "tl")+
  coord_sf(crs = 32631)+
  labs(colour = "speed (m/s)")

@@

```{r}
# make combined walkthrough figure
figure_walkthrough <-
wrap_plots(
  list(
    fig_data_bbox, fig_speed_outliers, fig_median_smooth),
  design = "AB\nAC")+
  plot_annotation(tag_levels = "a",
                  tag_prefix = "(",
                  tag_suffix = ")")

@@

```{r}
fig_calib_residence <-
  ggplot()+
  geom_point(data = data_res, 
             aes(x, y),
             size = 5, shape = 2,
             alpha = 0.1)+
  geom_point(data = data_recurse,
             aes(x, y, 
                 col = res_time > 5,
                 size = res_time > 5),
             shape = 19, alpha = 0.4,
             show.legend = F)+
  geom_path(data = data_recurse,
             aes(x, y),
            col = "grey", lwd = 0.2)+
  scale_colour_manual(values = c("grey40", pal[3]))+
  scale_size_manual(values = c(0.5, 2))+
  ggspatial::annotation_scale(location = "br")+
  ggthemes::theme_few()+
  theme(axis.text = element_blank(),
        axis.title = element_blank(),
        panel.background = element_rect(fill = "white"))+
  coord_sf(crs = 32631)
```

@@

```{r}
# patch with residence points and all patches
fig_basic_residence <-
  ggplot()+
  geom_sf(data = griend)+
  geom_point(data = data_res_summary, 
             aes(x_median, y_median),
             size = 10, shape = 7,
             # stroke = ,
             col = "grey20",
             alpha = 1)+
    # geom_path(data = data_recurse,
    #          aes(x, y),
    #         col = "grey", lwd = 0.2)+
  # geom_text(data = data_res_summary,
  #           aes(x_median, y_median,
  #               label = tID),
  #           # size = 10, shape = 7,
  #           # stroke = ,
  #           nudge_x = 100,
  #           fontface = "bold",
  #           col = "grey20",
  #           alpha = 1)+
  # geom_text(data = patch_summary_data, 
  #           aes(x_median, y_median,
  #               label = patch),
  #           # size = 10, shape = 7,
  #           # stroke = ,
  #           nudge_x = -50,
  #           fontface = "bold",
  #           col = pal[4],
  #           alpha = 1)+
  geom_point(data = data_recurse,
            aes(x, y,
                col = res_time > 5,
                shape = res_time > 5),
            show.legend = F,
            size = 2)+
  geom_sf(data = patch_sf_data,
          fill = pal[4],
          col = pal[4],
          alpha = 0.3)+
  # geom_segment(data = patch_summary_data,
  #           aes(x = x_end, y = y_end,
  #               xend = shift(x_start, type = "lag"),
  #               yend = shift(y_start, type = "lag")),
  #           col = pal[4], lty = 1,
  #           lwd = 0.5)+
  # geom_point(data = patch_summary_data,
  #            aes(x_median, y_median),
  #            size = 5,
  #            stroke = 1,
  #            col = pal[4],
  #            shape = 1,
  #            show.legend = F)+
  scale_colour_manual(values = c("grey40", pal[3]))+
  scale_shape_manual(values = c(1, 19))+
  scale_fill_distiller(palette = "RdPu")+
  ggspatial::annotation_scale(location = "tl")+
  ggthemes::theme_few()+
  theme(axis.text = element_blank(),
        axis.title = element_blank(),
        panel.background = element_rect(fill = "white"))+
  coord_sf(crs = 32631,
           expand = F,
           ylim = c(5901700, 5903150),
           xlim = c(649300, 650700))
```

>>>>

```{r}
# plot data
fig_data_bbox <-
  ggplot()+
  geom_path(data = data_raw,
            aes(x, y),
             col = "grey", alpha = 0.5, size = 0.3)+
  geom_point(data = data_raw,
             aes(x, y,
                 col = x > 645000),
             alpha = ifelse(data_raw$x > 645000, 0.5, 1),
             size = ifelse(data_raw$x > 645000, 0.3, 2),
             show.legend = F)+
  scale_colour_manual(values = c("grey", pal[3]))+
  geom_vline(xintercept = 645000,
             col = "grey", lty = 2)+
  ggspatial::annotation_scale(location = "br")+
  ggthemes::theme_few()+
  theme(axis.text = element_blank(),
        axis.title = element_blank())+
  coord_sf(crs = 32631)

@@

```{r}
# plot filtered data
fig_speed_outliers <-
  ggplot()+
  geom_point(data = data,
             aes(x, y, 
                 col = speed_in < 25.6),
             size = 0.3, alpha = 0.5,
             show.legend = F)+
  scale_color_manual(values = c("grey", pal[3]))+
  ggthemes::theme_few()+
  theme(axis.text = element_blank(),
        axis.title = element_blank())+
  ggspatial::annotation_scale(location = "tl")+
  coord_sf(crs = 32631)+
  labs(colour = "speed (m/s)")

@@

```{r}
# make combined walkthrough figure
figure_walkthrough <-
wrap_plots(
  list(
    fig_data_bbox, fig_speed_outliers, fig_median_smooth),
  design = "AB\nAC")+
  plot_annotation(tag_levels = "a",
                  tag_prefix = "(",
                  tag_suffix = ")")&
  theme(plot.tag = element_text(face = "bold"))

@@

```{r}
fig_calib_residence <-
  ggplot()+
  geom_point(data = data_res, 
             aes(x, y),
             size = 5, shape = 2,
             alpha = 0.1)+
  geom_point(data = data_recurse,
             aes(x, y, 
                 col = res_time > 5,
                 size = res_time > 5),
             shape = 19, alpha = 0.4,
             show.legend = F)+
  geom_path(data = data_recurse,
             aes(x, y),
            col = "grey", lwd = 0.2)+
  scale_colour_manual(values = c("grey40", pal[3]))+
  scale_size_manual(values = c(0.5, 2))+
  ggspatial::annotation_scale(location = "br")+
  ggthemes::theme_few()+
  theme(axis.text = element_blank(),
        axis.title = element_blank())+
  coord_sf(crs = 32631)
```

@@

```{r}
# patch with residence points and all patches
fig_basic_residence <-
  ggplot()+
  geom_sf(data = griend)+
  geom_point(data = data_res_summary, 
             aes(x_median, y_median),
             size = 10, shape = 7,
             # stroke = ,
             col = "grey20",
             alpha = 1)+
    # geom_path(data = data_recurse,
    #          aes(x, y),
    #         col = "grey", lwd = 0.2)+
  # geom_text(data = data_res_summary,
  #           aes(x_median, y_median,
  #               label = tID),
  #           # size = 10, shape = 7,
  #           # stroke = ,
  #           nudge_x = 100,
  #           fontface = "bold",
  #           col = "grey20",
  #           alpha = 1)+
  # geom_text(data = patch_summary_data, 
  #           aes(x_median, y_median,
  #               label = patch),
  #           # size = 10, shape = 7,
  #           # stroke = ,
  #           nudge_x = -50,
  #           fontface = "bold",
  #           col = pal[4],
  #           alpha = 1)+
  geom_point(data = data_recurse,
            aes(x, y,
                col = res_time > 5,
                shape = res_time > 5),
            show.legend = F,
            size = 2)+
  geom_sf(data = patch_sf_data,
          fill = pal[4],
          col = pal[4],
          alpha = 0.3)+
  # geom_segment(data = patch_summary_data,
  #           aes(x = x_end, y = y_end,
  #               xend = shift(x_start, type = "lag"),
  #               yend = shift(y_start, type = "lag")),
  #           col = pal[4], lty = 1,
  #           lwd = 0.5)+
  # geom_point(data = patch_summary_data,
  #            aes(x_median, y_median),
  #            size = 5,
  #            stroke = 1,
  #            col = pal[4],
  #            shape = 1,
  #            show.legend = F)+
  scale_colour_manual(values = c("grey40", pal[3]))+
  scale_shape_manual(values = c(1, 19))+
  scale_fill_distiller(palette = "RdPu")+
  ggspatial::annotation_scale(location = "tl")+
  ggthemes::theme_few()+
  theme(axis.text = element_blank(),
        axis.title = element_blank())+
  coord_sf(crs = 32631,
           expand = F,
           ylim = c(5901700, 5903150),
           xlim = c(649300, 650700))
```
